\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2012-09-03 smurf_paper.tex
a partial commit of algo section

Given \scuba's data rate, SMURF was designed with two primary goals in
mind: (i) reduced maps should be scientifically useful and of ``near
publication quality'' with minimal user interaction; and (ii) the
execution time should not appreciably exceed the amount of time
required to conduct observations on a high-end multi-tcore desktop
computer. By attaining these goals it would be possible to conduct
real-time reductions at the telescope to offer feedback to observers,
and it would also be possible to maintain a central repository of
(nearly) publishable data products.

As described in the introduction, rather than pursue a slow but
potentially more accurate \emph{maximum likelihood} method that would
require the inversion of a complex linear problem, we instead use an
iterative approach that estimates and removes most of the correlated
(and in particular low-frequency) noise sources in parallel with a
simplified map estimation. We do note, however, that recent advances
in direct inversion methods such as SANEPIC \citep{patanchon2008} may
in fact be tenable for \scuba\ data. A future goal of the software
team is to investigate meshing SMURF (perhaps as a cleaning step and
initial condition) for a SANEPIC-like algorithm.

>>>>

As described in the introduction, the approach taken by SMURF to
reducing \scuba\ data is to model (and remove) noise sources, and to
iterate this process along with estimates of the map. This sort of
algorithm has been used successfully in the past with instruments
including SCUBA \citep{1999ASPC..172..171J}, SHARC-2
\citep{kovacs2008}, and BOLOCAM \citep{aguirre2010}, and is capable of
recovering modest angular scales up to of order the footprint of the
array (depending, of course, on the noise in the data). The main
benefit of this approach over CMB-style maximum-likelihood methods
(which are generally superior at recovering structure on all scales
available in the data) is that the computing resources are
significantly smaller, both in terms of memory usage and execution
time. Given the massive volume of \scuba\ data produced in a single
observation (a rate of approximately 10 GB\,hr$^{-1}$ in each focal
plane), iterative techniques were the only viable option for providing
real-time feedback at the telescope, and for automatically reducing
near-science grade maps on a timescale comensurate with the
observation times using standard high-end desktop computers.  We do
note, however, that recent advances in direct inversion methods such
as SANEPIC \citep{patanchon2008} may in fact be tenable for \scuba\
data. A future goal of the software team is to investigate meshing
SMURF (perhaps as a cleaning step and initial condition) with a
SANEPIC-like algorithm.

Significant experimentation with different models for noise sources
during \scuba\ commissioning required a highly flexible software
framework with a simple (though extensive) interface for user
configurability. Though written in C, \smurf\ uses an object-oriented
style of handling the

As we have seen in Sections~\ref{sec:bolosignal}--\ref{sec:pca}
